Topological approach to finding blackholes in directed networks

### 2019-12-02 blackholes/pavt/article.tex
Blackholw search

%
\subsection{Related work}
%

@@

In this article we use to use the following algorithm for finding graph condensation.\par

First, we find topological sort of the initial graph. It takes O(E + V).
\begin{definition}
TODO: Topolorgical sort
\end{definition}

\begin{definition}
TODO: Closure
\end{definition}

@@

%
\subsection{Graph topology}
%

@@

%
% ---- Bibliography ----
%
\bibliographystyle{spmpsci}
\begin{thebibliography}{6}
%

\bibitem {a1:a2}
Example
\doi{doi:number}

\bibitem {onlyurl}
NCBI: National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}
\end{document}

>>>>

%
\subsection{Related work}
\cite{li2010detecting,li2012mining,li2014mining,hong2015detecting}

@@

In this article we use the following algorithm for finding graph condensation.
It was independently proposed by Kosaraju and Sharir back in 1979.\par 
First, we find topological sort of the initial graph. It takes O(E + V).
\begin{definition}
TODO: Topological sort
\end{definition}

\begin{definition}
Closure of vertex v is a set of all nodes reachable from v, including v.
\end{definition}

@@

%
\subsection{Blackholes search}
When the graph is prepared, we can move on to searching blackholes. The task is combinatorial in its nature, therefore, we aim to
decrease the number of potential black holes.
To understand the issue, we first describe BruteForce approach. \par

\begin{definition}
TODO: simple blackhole
\end{definition}

\begin{definition}
TODO: root of blackhole
\end{definition}

\begin{definition}
TODO: basis of blackhole
\end{definition}

\begin{definition}
TODO: complex blackhole
\end{definition}

\begin{definition}
TODO:
\end{definition}

To BruteForce the task we iterate over all possible unordered sets of nodes. 
Then for every node we acquire its closure. Union of all such closures is a candidate blackhole.
If candidate blackhole is a weakly connected subgraph, then it is a blackhole.

With BruteForce algorithm it is possible to find the same blackhole several times.
We aim to avoid at least some of the duplicates and introduce heuristic for it.

According to the definitions above if some node is not a root of blackhole, it can be omitted, as set of roots
uniquely identify a blackhole.
Every non-root node in blackhole is reachable from one of the roots. Therefore, if we know reachability matrix for
the given graph, we can skip bloated non-basis combinations of nodes.
Of course, we could straightforward build the reachability matrix. But, it takes O(V \^ 3) time. Even though we decreased graph size
in preprocessing step, it still can result in lots of computation. That is why, we will only try to partially skip duplicates and the rest will
be filtered later.\par

Let's consider a closure of a single blackhole root. Let this closure to be acquired by depth-first search, which, basically means, that
we can lay those nodes in topologically sorted order. Also, while traversing this graph, we can calculate size of closure for each node
in the given roots closure. Finally, if some node lays on the i'th position on the topological sort and its closure size is i, than we can
be conclude, that every node with index less than i in the topological sort will be reachable from v(i).

@@

%
% ---- Bibliography ----
%
\bibliographystyle{spmpsci}
\bibliography{biblio}

\end{document}
